---
title: "Case Study"
author: "Jeremy Otsap"
date: "June 26, 2019"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### loading libraries

library(dplyr)
library(ggplot2)
library(tidyr)
library(tidyverse)
library(reshape2)


```

## Data Sets

Here we are loading the beers and breweries data sets directly from their github repositories

```{r, echo=TRUE}

url<-"https://raw.githubusercontent.com/BivinSadler/MSDS-6306-Doing-Data-Science/master/Unit%207/Beers.csv"
beers <- read.csv(url(url), sep = ",", header = TRUE)
head(beers) 

url<-"https://raw.githubusercontent.com/BivinSadler/MSDS-6306-Doing-Data-Science/master/Unit%207/Breweries.csv"
brew <- read.csv(url(url), sep = ",", header = TRUE)
head(brew) 

```


### Beers.csv:
Name: Name of the beer.
Beer_ID: Unique identifier of the beer.
ABV: Alcohol by volume of the beer.
IBU: International Bitterness Units of the beer.
Brewery_ID: Brewery id associated with the beer.
Style: Style of the beer.
Ounces: Ounces of beer.

### Breweries.csv:
Brew_ID: Unique identifier of the brewery.
Name: Name of the brewery.
City: City where the brewery is located.
State: U.S. State where the brewery is located.


## INTRODUCTION

We are looking at data for popular brands of beers, as well as a collection of breweries throughout the US. Given these datasets we are looking to gain a better understanding of drinking preferences as well as brewery demographics.


## QUESTION 1: BREWERIES PER STATE

In the following code we count the number of breweries per state. We assign this information into the numBreweries dataframe and then order the data in descending order by the nunber of breweries. Colorado and California have the highest number of breweries. DC, North Dakota, South Dakota, and West Virginia are the lowest with only one brewery for the entire state. 


```{r, echo=TRUE}

# changing from factor to char
brew$State <- as.character(brew$State)
# changing to int
brew$Brew_ID <- as.integer(brew$Brew_ID)
# changing to char
brew$Name <-  as.character(brew$Name)

# removing trailing whitespace with str_trim
str_trim(brew$State, side = "left") -> brew$State
brew %>% group_by(State) %>% summarize(numBreweries = n_distinct(Name)) -> numBreweries
numBreweries <- arrange(numBreweries, desc(numBreweries))
tail(numBreweries)

```


Number of breweries by state

```{r, echo=TRUE}

# creating chart for breweries
numBreweries %>% ggplot(aes(x = State, y = numBreweries, fill = State)) + geom_col() + labs(title = "Breweries Per State") + theme( axis.text = element_text(size = rel(0.4)) )

```


## QUESTION 2: MERGED DATA SET

In the following code we merge beer data with the breweries data using the Brewery's Unique ID. To validate we successfuly combined these two data sets, We print the first eix and the last six observations. This will now allow us to further explore the dataset and examine potential correlations between the specific qualities of the beer and the demographics of the breweries which created them.


```{r, echo=TRUE}

combined <- merge(brew, beers, by.x = "Brew_ID", by.y = "Brewery_id")

# renaming Name.x to Brewery_Name
colnames(combined)[2] <- "Brewery_Name"
# renaming Name.y to Beer_Name
colnames(combined)[5] <- "Beer_Name"

head(combined, 6)
tail(combined, 6)

```


## QUESTION 3: MISSING DATA

In the following chunk code we report the number of missing values (listed as "NA") for each parameter. NA_count is the amount of NA in each column in the combined dataset. while only there are only 62 missing value in ABV (less than 3%) there were 1005 missing values in IBU-- over 40%. Therefore as we proceed we recommend caution on any graphs or analysis made involving the bitterness attribute

```{r, echo=TRUE}

na_count <-sapply(combined, function(y) sum(length(which(is.na(y)))))
na_count

```



## QUESTION 4: MEDIAN ALCOHOL CONTENT

We compute the median for both alcohol content [ABV] and bitterness [IBU] for each state. In order to do this we first grouped the combined dataset by State, then sumarized that grouped data calculating the median for ABV and IBU. NA values were ignored and the resulting data was put into a dataframe called "plot1." We then created the chart below to visualize this data where the height represents the alcohol content and the darkness of color represents the bitterness

```{r, echo=TRUE}

# data first grouped by state
# then piped to summarize function which aggregates on median() function
# note that NA values were ignored
combined %>% group_by(State) %>% summarize(Alcohol_content = median(ABV, na.rm = TRUE), Bitterness= median(IBU, na.rm = TRUE)) -> plot1
plot1

ggplot(plot1, aes(x=reorder(State,-Alcohol_content),y=Alcohol_content, fill=Bitterness)) + geom_bar(stat="identity") + coord_flip(ylim=c(.04,.0650)) + theme(legend.position='none') + scale_fill_gradient2(midpoint=median(plot1$Alcohol_content), space='Lab') + theme_classic()+labs(x="State", y="ABV", legend="ABV")+ ggtitle("Median ABV by state") + theme(plot.title = element_text(hjust = 0.5),axis.text=element_text(size=5)) 

```


Additionally, we also created tables to quickly show top 5 and bottom 5 for ABV and IBU


The top 5 states for median alcohol content

```{r, echo=TRUE}

### CORRECT DATA ###
head(plot1[order(plot1$Alcohol_content, decreasing = T, na.last = T),],5) 

```


The top 5 states for bitterness

```{r, echo=TRUE}

### CORRECT DATA ###
head(plot1[order(plot1$Bitterness, decreasing = T, na.last = T),],5) 

```


The bottom 5 states for median alcohol content

```{r, echo=TRUE}

### CORRECT DATA ###
head(plot1[order(plot1$Alcohol_content, decreasing = F, na.last = T),],5) 

```


The bottom 5 states for bitterness

```{r, echo=TRUE}

### CORRECT DATA ###
head(plot1[order(plot1$Bitterness, decreasing = F, na.last = T),],5) 

```



## QUESTION 5: MAX IBU & ABV STATES

The following code show the beer with the highest raw [NOT median] alcohol content and bitterness. Additionally shows its various attributes such as which brewery distills it, what state that brewery is in, and the style of beer. 


Individual Beer with Highest Alcohol Content**  
_**Note that bitterness information is unavailable_

```{r, echo=TRUE}

head(beers[order(beers$ABV, decreasing = T, na.last = T),],1)

```


Individual Beer with Highest Bitterness

```{r, echo=TRUE}

head(beers[order(beers$IBU, decreasing = T, na.last = T),],1)

```




## QUESTION 6: SUMMARY STATS FOR ABV

Below we show the distribution of alcohol content across all beers in our data set. Again the NA values need to be removed from our data. Additionally we represent this visually with a boxplot.


```{r, echo=TRUE}

#find NA
which( !is.na(beers$ABV) ) -> beers_na

#assign santized data to new variable
beers$ABV[beers_na] -> beers_abv

#summerize & plot sanitized data
summary(beers_abv)

boxplot(beers_abv, main=toupper("Alcohol Content in Beers"), font.main=3, cex.main=1.2, xlab="Beers", ylab="Alcohol Content", font.lab=3, col="blue")

```



## QUESTION 7: ABV & IBU RELATIONSHIP

Here we examine to see if there is evidence of a correlation between a beer's alcohol content and its bitterness. We do a correlation test which shows there is evidence of a moderate correlation of 67.06% between them [p-value < 0.0001]. We also plot this and calculate the regression line, with an estimated R-squared is 44.97%, which means almost 45% of a beer's bitterness can be accounted for by its alcohol content. As with prior analysis the NA values will be ignored


```{r, echo=TRUE}

# tests R correlation between ABV & IBU ignoring NA entries
cor.test(combined$ABV, combined$IBU, na.action(na.omit("NA")))

#predicting bitterness based on alcohol content
beer.lm <- lm(combined$IBU ~ combined$ABV, na.action(na.omit("NA")))
summary(beer.lm)

```


Scatterplot and regression line between alcohol & bitterness

```{r, echo=TRUE}
plot(combined$ABV, combined$IBU, xlab = "Alcohol Content", ylab = "Bitterness")
abline( lm(combined$IBU ~ combined$ABV)  , col = "red")
```




Additionally we looked at the most popular style of beer across the US which turned out to be American IPA; having close to twice as many different individual beers as the second most popular.


```{r, echo=TRUE}

beers %>% count(Style) %>% arrange(desc(n)) -> beers_style
head(beers_style[order(beers_style$n, decreasing = T, na.last = T),],5)

```



## CONCLUSION

Given the combination of factors, my recommendation is for West Virginia. Currently there is only 1 brewery for the entire state, and of the bottom four states which all had only 1 brewery, West Virginia has the highest population.  Nationwide the average ratio of brewery to people was 1-2 breweries per million residents. West Virginia was below this at around 0.553. Furthermore this brewery does not make an American IPA, the most popular style.

As shown by the prior analysis, it was in the top for both highest median ABV and highest median IBU. Thus this may be a good opportunity to have a native brewery making a less bitter American IPA. 

There are also additional factors: West Virginia has one of the lowest economies of any US state. This means high unemployment and very inexpensive real-estate. Its fairly reasonable to anticipate a high level of cooperation from the local government given their need as well as recent appeals for more industry. On a final note they also have large natural gas reserves, which could be an added bonus to the company looking for a more eco-friendly energy source.

