---
title: "Case Study 1"
author: "Fabio"
date: "6/24/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
source("Case_study_Codebook.R")
knitr::opts_chunk$set(echo = FALSE)
```


## Case Study 1

-Bitterness & Concentration Across US Breweries

-SMU - DDS 6306

-Members: 
  
  Fabio Savorgnan
  
  Jeremy Otsap


## Overview
-Beer Data Set                                                     

Name: Name of the beer.
Beer_ID: Unique identifier of the beer.
ABV: Alcohol by volume of the beer.
IBU: International Bitterness Units of the beer.
Brewery_ID: Brewery id associated with the beer.
Style: Style of the beer.
Ounces: Ounces of beer.

-Brewery Data Set

Brew_ID: Unique identifier of the brewery.
Name: Name of the brewery.
City: City where the brewery is located.
State: U.S. State where the brewery is located.
  
## Introduction: Given the datasets Beer and Brews, we want to know

-Where our headquarters should be?

-What style and name of beer would appeal to the widest audience?

-What ABV and IBU should be used for the production of beers?


## Combined Data Set
 -The first 6 aoservations
 
```{r,message=F, warning = F }
library(kableExtra)
head(combined, 6)
``` 
## Combined Data Set
-The last 6 observations

```{r,message=F, warning = F }
library(kableExtra)
tail(combined, 6)
``` 

## Missing values

-Alcohol by Volume – 62 of 2410 entries were missing. ~2.57%

-International Bitterness – 1005 of 2410 entries were missing. ~41.7%

-NOTE: Bitterness data not available for South Dakota


```{r }
na_count
``` 
## Breweries Per State
Top 4 States: -Colorado -California -Michigan -Oregon

Bottom 4 States: -DC -South Dakota -North Dakota -West Virginia
```{r }
g6
``` 


## Median Alcohol & Bitterness By State

```{r }
g7
``` 

## The top 5 state with more alcohol content


```{r }
x1
```

## The top 5 state with the most bitter beer

```{r }
x2
```


## The bottom 5 lowest state with alcohol content

```{r }
x3
```


## The bottom 5 lowest state with bitterness per beer

```{r }
x4
```

## Alcohol Content
  -Lee Hill Series Vol. 5 - Belgian Style Quadrupel Ale
  
  -12.8% AB
  
  -Colorado
```{r, echo=FALSE}
boxplot(beers$ABV, main=toupper("Alcohol Content in Beers"), font.main=3, cex.main=1.2, xlab="Beers", ylab="Alcohol Content", font.lab=3, col="darkgreen")
```

## Highest Bitterness Beer
-Bitter Bitch Imperial IPA

-IBU of 138

-Oregon
```{r,echo=FALSE }
boxplot(beers$IBU, main=toupper("Bitterness in Beers"), font.main=3, cex.main=1.2, xlab="Beers", ylab="Bitterness", font.lab=3, col="darkgreen")
```


## Correlation Between Bitterness & Alcohol Content

-Correlation: 67.06%

-R-squared: 44.97%

-This shows a moderate correlation between the bitterness and strength of the alcohol. About 45% of the bitterness of a particular beer is accounted for by its alcohol content

## Plot of the Relationship Between Bitterness & Alcohol Content

```{r, echo=FALSE }
grid(plot(combined$ABV, combined$IBU, main="Scatterplot Between Alcohol Content & Bitterness", xlab = "Alcohol Content", ylab = "Alcohol Bitterness"))
```

## Additional Analysis : 2018 Census Data on https://www.census.gov 

-Examining correlation between state population and number of breweries

-There appears to be a moderate correlation of 62.1%

-The R-squared value is 38.57% which means that almost 39% of the brewery density can be explained by the respective state’s total population

## Plotting the correlation between state population and number of breweries

```{r,echo=FALSE }
grid(plot(combined_pop$Population, combined_pop$numBreweries,main="Relationship of Breweries & Total Population", xlab = "Population by State", ylab = "Number of Breweries"))
abline(brew_pop.lm, col = "red")
```

## Additional Analysis : 2018 Census Data on https://www.census.gov 

-Examining correlation between number of breweries and median alcohol content

```{r, echo=FALSE }
numBreweries<-as.data.frame(numBreweries)
plot1<-as.data.frame(plot1)
albrew<- merge(plot1,numBreweries, by= "State")
head(albrew)%>% kable %>% kable_styling(bootstrap_options = 'striped')
```
## Plotting the correlation between number of breweries and median alcohol content

```{r, echo=FALSE }
grid(plot(albrew$numBreweries, albrew$Alcohol_content, main="Relationship Median Alcohol and Breweries", xlab = "Number of Breweries", ylab = "Median Alcohol Content"))
abline(brew_pop.lm, col = "red")
```

## Additional Analysis : 2018 Census Data on https://www.census.gov 

-Examining correlation between population and median alcohol content

```{r, echo=FALSE }
merge(albrew, state_population, by = "State") ->alpop 
head(alpop)%>% kable %>% kable_styling(bootstrap_options = 'striped')
```

## Plotting the  correlation between population and median alcohol content

```{r, echo=FALSE }
grid(plot(alpop$Population, alpop$Alcohol_content, main="Relationship Median Alcohol and Population", xlab = "Population", ylab = "Median Alcohol Content"))
abline(brew_pop.lm, col = "red")
```

## Most popular beer style in the US

Most popular beer  style in the US: American IPA. 

```{r, echo=FALSE }
beers %>% count(Style) %>% arrange(desc(n)) -> BeersStyle
head(BeersStyle, 1)%>% kable %>% kable_styling(bootstrap_options = 'striped')
```

## Most popular beer name in the US

Most popular beer name in the US: Nonstop Hef Hop

```{r, echo=FALSE }
beers %>% count(Name) %>% arrange(desc(n)) -> BeersName
head(BeersName,1)%>% kable %>% kable_styling(bootstrap_options = 'striped')
```


## Conclusion 1

-We will recommend to have the headquarter in a state with the lowest amount of breweries which is Mississippi

-The style of beer that we would recommend will be American IPA. We found American IPA to be the most
 popular style

-The name of the beer that we will recommend will be Nonstop Hef Hop. We found Nonstop Hef Hop to be 
the most popular beer name

-According to our statistic summary from ABV and IBU , for an average ABV beer at 0.06 the recommended
IBU is roughly 40.

-We will recommend to target the states with less breweries regardless of the population, because we did not find 
any strong  correlation between the population and the amount of breweries


## The End
