---
title: "Beer Study"
author: "Fabio Savorgnan"
date: "6/24/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
source("Case_study_Codebook.R")
knitr::opts_chunk$set(echo = FALSE)
```


## Beer Study

- ***Breweries in the US Territory***

- ***Members:*** 
  
  Fabio Savorgnan
  
  Jeremy Otsap


## Overview{.columns-2}
- **Beer Data Set**

Name

Beer_ID

ABV

IBU

Brewery_ID

Style 

Ounces 

- ***Brewery Data Set***

Brew_ID 

Name 

City 

State
  
## Introduction: Given the datasets Beer and Brews, we want to know

- ***Where our headquarters should be?***

- ***What style and name of beer would appeal to the widest audience?***

- ***What ABV and IBU should be used for the production of beers?***


## Combined Data Set
 - ***The first 6 observations***
 
```{r,message=F, warning = F }

library(kableExtra)
head(combined, 6)%>% kable %>% kable_styling(bootstrap_options = c('striped', 'condensed'), font_size = 8)

``` 
## Combined Data Set
- ***The last 6 observations***

```{r,message=F, warning = F }

library(kableExtra)
tail(combined, 6)%>% kable %>% kable_styling(bootstrap_options = c('striped', 'condensed'), font_size = 8)

``` 

## Missing values

- ***Alcohol by Volume – 62 of 2410 entries were missing.***

***~2.57%***

- ***International Bitterness – 1005 of 2410 entries were missing.*** 

**~41.7%***

- ***NOTE: Bitterness data not available for South Dakota***


```{r }
na_count%>% kable %>% kable_styling(bootstrap_options = c('striped', 'condensed'), font_size = 11)
``` 
## Breweries Per State
***Top 4 States:*** -Colorado -California -Michigan -Oregon

***Bottom 4 States:*** -DC -South Dakota -North Dakota -West Virginia
```{r }
p3 
``` 


## Median Alcohol & Bitterness By State

```{r }
g7
``` 

## The top 5 state with more alcohol content


```{r }
x1+ theme_minimal()
```

## The top 5 state with the most bitter beer

```{r }
x2 + theme_minimal()
```


## The bottom 5 lowest state with alcohol content

```{r }
x3 + theme_minimal()
```


## The bottom 5 lowest state with bitterness per beer

```{r }
x4 + theme_minimal()
```

## Alcohol Content 
  - ***Lee Hill Series Vol. 5 - Belgian Style Quadrupel Ale***
  - ***12.8% AB***
  - ***Colorado***
```{r, echo=FALSE }
boxplot(beers$ABV, main=toupper("Alcohol Content in Beers"), font.main=3, cex.main=1.2, xlab="Beers", ylab="Alcohol Content", font.lab=3, col="darkgreen") 
```

## Highest Bitterness Beer 
- ***Bitter Bitch Imperial IPA***
- ***IBU of 138***
- ***Oregon***
```{r,echo=FALSE }
boxplot(beers$IBU, main=toupper("Bitterness in Beers"), font.main=3, cex.main=1.2, xlab="Beers", ylab="Bitterness", font.lab=3, col="darkgreen") 
```


## Relationship Between Bitterness & Alcohol Content {.columns-2}

- ***Correlation: 67.06%***

- ***R-squared: 44.97%***

- ***This shows a moderate correlation between the bitterness and strength of the alcohol. About 45% of the bitterness of a particular beer is accounted for by its alcohol content***

```{r, echo=FALSE , out.width='450px'}
grid(plot(combined$ABV, combined$IBU, main="Scatterplot Between Alcohol Content & Bitterness", xlab = "Alcohol Content", ylab = "Alcohol Bitterness"))

```


## Examining correlation between state population and number of breweries {.columns-2} 

- ***There appears to be a moderate correlation of 62.1%***

- ***The R-squared value is 38.57% which means that almost 39% of the brewery density can be explained by the respective state’s total population***

```{r, echo=FALSE, out.width='450px' }
grid(plot(combined_pop$Population, combined_pop$numBreweries,main="Relationship of Breweries & Total Population", xlab = "Population by State", ylab = "Number of Breweries"))
abline(brew_pop.lm, col = "red") 

```

## Most popular beer style and name in the US

- Most popular beer style

- Most popular beer name in the US

```{r, echo=FALSE }
beers %>% count(Style) %>% arrange(desc(n)) -> BeersStyle
head(BeersStyle, 1)%>% kable %>% kable_styling(bootstrap_options = 'striped') 
beers %>% count(Name) %>% arrange(desc(n)) -> BeersName
head(BeersName,1)%>% kable %>% kable_styling(bootstrap_options = 'striped') 
```



## Conclusion 

- ***Headquarter in West Virginia.***

- ***The style of beer American IPA. ***

- ***The name of the beer Nonstop Hef Hop.***

- ***For an average ABV beer at 0.06 the recommended IBU is roughly 40.***



## Questions
